Network Analysis of Code Similarity

### 2014-11-21 network-analysis.Rmd
Plot options and community detection

```{r}
g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar=c(0,0,0,0))
plot(g, edge.width = E(g)$weight * 12, layout = l, edge.arrow.size= 0.25, vertex.size = 5)
```

>>>>

```{r}
g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar=c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 10, layout = l,
     edge.arrow.size= 0.15, vertex.size = 5)
title("Codes of Civil Procedure")
```

Community detection

```{r}
g %>%
  walktrap.community() %>%
  plot(., g, vertex.label = NA, layout = l, vertex.size = 3)
```
